Iterative Monomorphisation

### 2024-02-14 iterative_monomorphisation.tex
added everything?
abstrac

\sloppy

@@

\begin{abstract}
   Monomorphisation methods allows the extension of some higher order theorem provers to polymorphic logics. This paper presents an iterative approach to monomorphisation with two main goals: creating an efficient method for extending higher order provers to polymorphic logics and improving the performance of existing provers which natively support polymorphism.

   We first present the iterative monomorphisation algorithm, before discussing its implementation in Zipperposition. Finally, the implementation is evaluated as an alternative to native polymorphism and as a means to strenghen Zipperposition.
\end{abstract}

@@

This algorithm is implemented in Zipperpostion, a higher order polymorphic automatic theorem prover written in OCaml. This implementation allows for the E prover, which does not support polymorphism, to be used as a backend to Zipperposition. The viability of this approach is then evaluated, both as an improvement to Zipperposition and as a means to increase the performance of other provers.

>>>>

%\sloppy

@@

\begin{abstract}
Monomorphisation makes it possible to extend monormophic provers to support
polymorphic logics. We propose an iterative approach, which is necessarily
incomplete but which works well in practice. It is implemented in the
Zipperposition prover, where it can be used to translate away polymorphism
before invoking a monomorphic prover. Our empirical evaluation reveals that
iterative monorphisation is a viable alternative to native polymorphism.
\end{abstract}

@@

This algorithm is implemented in Zipperpostion, a higher order polymorphic automatic theorem prover written in OCaml. As a result, the E prover, which does not support polymorphism, can be used as a backend to Zipperposition. The viability of this approach is then evaluated, both as an improvement to Zipperposition and as a means to increase the performance of other provers.
